\documentclass[12pt, titlepage]{article}
\usepackage{graphicx} % Required for inserting images
\usepackage[skip=10pt, indent=0pt]{parskip}
\usepackage[a4paper, total={6in, 9in}]{geometry}
\usepackage [english]{babel}
\usepackage [autostyle, english = american]{csquotes}
\MakeOuterQuote{"}
\usepackage{setspace}
\doublespacing
\usepackage{float}
\usepackage{url}
\usepackage{glossaries}
\usepackage{outlines}
\usepackage{lipsum}

\newacronym{eaits}{EAITS}{Ever After in the Stars}


\title{THE EVER AFTER IN THE STARS COMPENDIUM}
\author{Manu Abella, Eugene Briones}
\date{2024-}

\setcounter{tocdepth}{2}

\begin{document}

\maketitle


\tableofcontents
\newpage

\section{Introduction}

\gls{eaits}

\section{Characters}

\subsection{Pandora}

\subsection{Valeria}

\subsection{Nox}

A genocidal maniac hell bent on his ambitions. He is a major antagonist for a significant portion of the chronology of the \gls{eaits} universe. He is a large, imposing figure with a santa-like, fatherly attitude most of the time. He can have an instant switch to an intimidating character, fittingly so, as he is responsible for the conquering and murders of millions and billions. 

\subsection{33}

\subsection{Miscellaneous small characters}

\section{World-Building}

\begin{outline}
    \1 Imperial Factions
        \2 Isolationists
            \3 Imperial grp going planet to planet to maintain the planet's separation from others
            \3 They gatekeep from other factions
            \3 Other factions idea is unification
            \3 Anti-colonial
            \3 Paradox: Anti-colonial but colonizes
            \3 Paradox: Believes in no interference, but  the action of imposing no interference, IS interference
        \2 Nox's Empire
            \3 
        \2 Valeria's Empire
            \3 Like the isolationists
            \3 Takes over diff. planets
            \3 she lets them go abt their natural destiny
            \3 planets are judged every so often
            \3 at some point, they will reveal themselves 
        \2 Regulus' Empire
            \3 Embodies all of the systemic with the stars
            \3 racism, slavery, etc. 
            \3 Regulus and his boys at the top
                \4 intellectuals, highest tier planet origins
            \3 believes in a manifest destiny for the universe
            \3 its the empire that proves why there needs to be better ones
\end{outline}

\subsection{Planets}

\subsubsection{Planet: ""}

There was a guy who invented a capsule that keeps you alive indefinitely. You go inside, get locked in forever, and are put into a simulation of your idea of heaven
To discover what form of pleasure you respond to the most, you are put through a series of random scenarios and tests over the course of a year or something, and someone on the outside monitors your emotions through your heart rate and your neural pathways or whatever.
All of the capsules are controlled by a selective group of people that act as their guardians and maintainers. Thing is, when this technology was discovered it was the only immortality tech on that planet. This meant that while 90\% of the population of the planet was placed into these capsules, the people mainting the capsules would eventually die, so they had to pass on the mantle of being one of the capsules guardians generationally
This is how it went, until this planet was discovered by the larger OT universe 

\subsubsection{Planet: "Lepton"}
Planet: "Lepton" Formerly known as "Lumira" before the company took over

A monolopy corporation (named Lepton) that ran the entire thing that eventually decayed. Literal corporate wasteland 

\subsubsection{Stratos-34 a.k.a. "Heaviside"}

On Stratos-34 a.k.a. "Heaviside" war has been brewing.

Heaviside is run as a global hegemony by The Jellicle Coalition, and is currently in conflict with a religon-led separatist faction "Whisper" that's declared independence citing the coalition's oppressive authoritarian rule. Whisper is currently operating from it's two moons which Whisper calls Shizuku and Seiji (though the Coalition refers to them as Mungojerrie and Rummpleteazer).

They currently engage in guerilla warfare on multiple fronts on Heaviside (most notably, the cavalry of the Coalition and the cavalry of Whisper clashing to a standstill in the no-man's land of Gallowgate) as well as in the space in between the moons and the planet referred to as The Terminal Layer.

The fighting has not stopped for eons. 

\subsubsection{Planet Flantith}

Visually speaking, it looks like crater from adventure time. A completely desolate planet due to the enormous bomb that was dropped. Another wasteland, yes, but this time it was due to an explosion. however, the catch is the explosion resulted in the death of all large liviing organisms, micro organisms are thriving. Materials are abundant. These resources would be of great preference to other planets, possibly allowing for large societal advancements. It is an enormous planet too, 500,000 earths, so the amount of resources available are effectively endless. It is unique because no other planet has found this one yet. It will, however, in the near future be discovered by another planet, one that is highly struggling in the progression department, which will be my next planet idea, hehe.

\subsubsection{Heroic woman planet}

On a planet in the cosmos lived a woman with unusual abilities. For some inexplicable reason, she was born with a curse. The woman could never be harmed or killed and she would never age. But for every day of her immortal life she had to repay the universe by killing another person. If she didn't, a ravenous hunger would completely overtake mind and she would kill everyone around her until she was satisfied. Nobody knows exactly why she was born with this curse, but some say that she can sometimes be spotted with a mysterious woman with pale skin and dark clothes. This woman could have easily gone down a dark path, but instead, she worked as hard as possible to live the most moral life she could given the circumstances. She gained the trust of the world around her, and at the present time, everyone on the planet knows about her curse and how to deal with it. She is given clearance to enter any hospital she can, so that she can kill terminally ill patients with a peaceful capsule with their full consent. She has also been given means of proving her own identity, so that imposters can't take advantage of the systems in place surrounding her. Of course, this also creates a laundry list of questions, but the biggest problem arises when their planet is finally discovered by the ships of the undying lands. When the option to become immortal is brought to the planet, what do she and the people around her do? 

\subsubsection{Snow Planet}

It's a planet that's frozen. There's a magical force or some bullshit that turns some of the show into sentient beings. These are the snow elves, and they can shapeshift. The snow elves are divided into 4 factions: The Snow Angels, The Malic Misers, The Mistletoe Machines, and The Jolly Lollipops

\subsubsection{Poor Planet}

A really really poor planet. in their last ditch efforts, they send out a team of adventurers and hunters to a distant planet they saw in their own solar system, and it is planet flantith. They extract all their resources from this planet, and several years later, completely converts into a thriving planet.

\subsubsection{Artist Planet}

This planet was terra formed to be a centre for artists across the universe to gain inspiration and conduct their work. You can rent and buy out spaces on the planet, and simulate any environment on the galactic database. From there, you can sketch out the environments, film scenes for movies, etc. It's every artist's dreamland

\subsubsection{Dark Lord Planet}

There was a planet that was ravaged by a wicked dark lord. The planet was liberated from it's cruel master by explorers from the undying lands, but even so most of the planet's history and culture were destroyed. After the surviving locals of the planet took one of the immortality elixirs, they went to the stars in search of a treasure. You see, before the dark lord destroyed everything, a time capsule containing the most important information about the planet's history, art, and culture was sent into space. These refugees are on a quest to find the capsule and restore their planet to it's former glory


\subsection{Organizations}

\subsubsection{Space pirate organization}

There was a space pirate organization that used uninhabitable planets as facilities for their operations. They would hide in underground tunnels, and  created rooms with artificial sunlight and carbon dioxide. There would be special rooms in these facilities that simulated various ecosystems, so that they could continuously gather resources and food. One of these planets was forgotten about and abandoned, because the space pirates that operated there were captured. Despite this, the technology lived on, and the life in those tunnels began to evolve. 

\section{Story/Plot Ideas}

\section{Call notes}

\subsection{Nov 2 Call}

\begin{outline}
    \1 How empires work
    \1 Random ideas:
        \2 Goron Nox
        \2 Stakes (AT) structure for 33 plot
        \2 dying lands and undying lands
\end{outline}

\end{document}
